Poseidon Adventure

### 2019-05-13 docs/index.Rmd
add CCA lf vis
add NOBA lf example, at long last

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/CCATrueLengthCompTest.html" target="_blank">CCA length composition examples - May 11, 2019</a>

But don't try running length comps at the subannual level for all species.

<a href="https://sgaichas.github.io/poseidon-dev/NOBATrueLengthCompTest.html" target="_blank">NOBA length composition examples - May 13, 2019</a>
